R Notebook

### 2020-01-31 src/comb-maxent.Rmd
messing with Remi's code... one plot still to fiddle with

>>>>

#2d maps

this is currently set to 0.5 cut-off... not SLR and MJ would like this changed

mcp <- st_read("../data/plot4-variables/minimum_convex_poly/mcp-wgs84.shp")

s <- st_read("../data/plot3-2d/landp/land-wgs84v2.shp") %>% 
  st_set_crs(proj) %>% 
  st_intersection(mcp)

filelist <- list.files("../data/plot3-2d/hotspot-mapping/",include.dirs = TRUE)

x <- stack(file.path("../data/plot3-2d/hotspot-mapping/",filelist)) %>% 
  mask(mcp) %>% 
  rasterToPoints() %>% 
  as.data.frame() %>% 
  gather(key = "variable", value = "value",-x,-y) %>% 
  mutate(month=factor(months(parse_date_time(gsub("_.*$", "",variable),"%m")),
                      ordered = TRUE,
                      levels=months(parse_date_time(1:12,"%m"))),
         value=ifelse(value==1,">0.5","<0.5"))

df <- x %>% 
  group_by(month) %>% 
  summarize(total=round(sum(value==">0.5")/n(),2))

ggplot(x)+
  geom_sf(data=s,fill='grey',colour='transparent')+
  geom_raster(aes(x,y,fill=value))+
  scale_fill_manual(values=c('transparent','red'))+
  geom_sf(data=mcp,fill="transparent")+
  geom_text(data=df,x=-50,y=67,label=df$total)+
  facet_wrap(~month,nrow=2)+#,
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold"))

ggsave("../output/maxent/paper_plots/two-d.png", height = 210, width = 297, units = "mm", dpi = 600)
```

### 2020-01-31 src/testing_file.Rmd
messing with Remi's code... one plot still to fiddle with

for(v in vars){
  if(v=='chl'){
  assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1 , 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+

           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           labs(title=sapply(v, CapStr))+ #i added

           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  }else if(v=='o2'){
      assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1 , 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title=sapply(v, CapStr))+ #i added

@@

ggsave("../output/maxent/paper_plots/variable_samples.png", height = 210, width = 297, units = "mm", dpi = 600)
```

@@

@@

ggplot(x)+
  geom_sf(data=s,fill='grey',colour='transparent')+
  geom_raster(aes(x,y,fill=value))+
  scale_fill_manual(values=c('transparent','red'))+
  geom_sf(data=mcp,fill="transparent")+
  geom_text(data=df,x=-50,y=67,label=df$total)+
  facet_wrap(~month,nrow=2)+#,
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1))
```

>>>>

for(v in vars){
  if(v=='chl'){
   assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
            scale_fill_viridis(option="viridis", direction = -1, 
             #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title= "Chl \u03b1")+ #i added
           facet_wrap(~monthyear,nrow=4,strip.position = "right")+
           theme_classic()+
           scale_x_continuous(breaks = seq(-70,-50,10))+
           theme(legend.position = "bottom",
                 axis.title.x=element_blank(),
                 axis.title.y=element_blank(),
                 axis.text.x=element_text(angle=45,vjust=1,hjust=1),
                 strip.background = element_blank(),
                 strip.text = element_blank()))
  }else if(v=='o2'){
      assign(v,ggplot(x %>% filter(variable==v,month!='September'))+
           geom_sf(data=s,fill='grey')+
           geom_raster(aes(x,y,fill=value))+
           geom_sf(data=mcp,fill="transparent")+
           scale_fill_viridis(option="viridis", direction = -1 , 
           #scale_fill_distiller(palette="Spectral", direction=-1)+
           guide_colourbar(barwidth=0.5, title = "mmol\u207B\u00B3", draw.ulim = FALSE, draw.llim = FALSE))+
           labs(title=paste0("Dissolved ", sapply(v, CapStr)))+ #i added

@@

#ggsave("../output/maxent/paper_plots/variable_samples.png", height = 210, width = 297, units = "mm", dpi = 600)
```

@@

#2-d map

@@

ggplot(x)+
  geom_sf(data=s,fill='grey',colour='transparent')+
  geom_raster(aes(x,y,fill=value))+
  scale_fill_manual(values=c('transparent','red'))+
  geom_sf(data=mcp,fill="transparent")+
  geom_text(data=df,x=-50,y=67,label=df$total)+
  facet_wrap(~month,nrow=2)+#,
  theme_classic()+
  scale_x_continuous(breaks = seq(-70,-50,10))+
  theme(legend.position = "none",
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        strip.background = element_blank(),
        strip.text.x = element_text(face = "bold"))

ggsave("../output/maxent/paper_plots/two-d.png", height = 210, width = 297, units = "mm", dpi = 600)
